### 2012-12-19 MSWL_ECO_lesson3.tex
updated #6 - Summary: Cost/benefit analysis
* Updated section "What disappears when a business uses libre software?"
* gitignore file avoiding eclipse texlipse project files.
* main file updated removing conflict

\subsection{What disappears when a business uses libre software?}

@@

\section{Conclusions}\label{conclusions}

>>>>

\section{What disappears when a business uses libre software?}

What brings us to a business using FLOSS technologies? What doors are open to us?

\begin{itemize}
    \item \emph{Dependence on monopolies:}
    \begin{itemize}
        \item Real competition, better products, better services. The technology is not dependent on a single supplier, technology is the union of different suppliers in oneself when using the product, it can become a provider of the same technology.
    \end{itemize}  
    \item \emph{Importance of vendor reliability:}
    \begin{itemize}
        \item Future depends on product acceptance in the market. The vendor is exposed to continuous product analysis by different users. In every field of use of the product are certain tests that help the overall assessment and therefore the acceptance thereof by users. This process causes the provider to increase its reliability with regard to the consumer.
    \end{itemize}  
    \item \emph{Decisions taken based on few elements:}
    \begin{itemize}
        \item Software can be tested in its real environment, at a very low cost. You have the possibility to imagine all kind of test in every environment you choose to check product capabilities and compare your results with other analysis.
    \end{itemize}  
    \item \emph{Dependence on the strategy of providers:}
    \begin{itemize}
        \item Decisions on the evolution of a product taken for those contributing with resources. You have the possibility to include your thought into the product roadmap, also you can improve with your contributions to the project and share ideas with the community in an cross-ideas open platform.
    \end{itemize}  
    \item \emph{Confidence on "black boxes":}
    \begin{itemize}
        \item Using FLOSS projects we can see the whole process of the data inside de technology, we don't have \emph{black holes} where we miss which operations are done. We do not lose the path of process operations being applied to our data the software from input to output. For example an application service like gmail. This application hides we treat our data to drive the process of sending an email and the result shows that message has been sent as output  
    \end{itemize}  
    \begin{figure}[h]
        \begin{center}
            \includegraphics{blackbox}
            \caption{BlackBox; we only can see the input and the output, not the process.}
            \label{fig:curve}
        \end{center}
    \end{figure}
\end{itemize}

\section{Conclusions}\label{lesson-3-conclusions}

@@
